---
title: "Descriptive analysis"
author: "Jae Yeon Kim"
output:
html_document: 
  toc: true
  theme: united
---

## 0. Setup 

I tweaked the global option of the R Markdown to enlarge figures produced by ggplot2.

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8, 
                      echo = FALSE, warning = FALSE, message = FALSE) # global setting for enlarging image size
```

```{r}

# Clean up the environment

rm(list = ls())

# Import libraries (adapted from this link: https://stackoverflow.com/questions/4090169/elegant-way-to-check-for-missing-packages-and-install-them)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
        tidyverse, # for the tidyverse framework
        patchwork, # for arranging ggplots 
        ggthemes, # for fancy ggplot themes
        
        ### For making maps (https://geocompr.robinlovelace.net/adv-map.html#animated-maps)
        
        sf,
        raster,
        spData, 
        tmap,     # for static and interactive maps
        leaflet,  # for interactive maps
        mapview,  # for interactive maps
        shiny,    # for web applications
        openintro # for abbr2state function 
)

```


## 1. Load files

N of Asian orgs: 299
N of Latino orgs: 519 

```{r}

# Load files

asian_org <- read_csv("/home/jae/analyzing-asian-american-latino-civic-infrastructure/raw_data/asian_orgs.csv")

latino_org <- read_csv("/home/jae/analyzing-asian-american-latino-civic-infrastructure/raw_data/latino_orgs.csv")

glimpse(asian_org)
glimpse(latino_org)
```

## 2. Descriptive analysis

### 2.1. Cross-sectional analysis

```{r}
aa_org_n <- asian_org %>%
  dplyr::select(City, Type) %>%
  group_by(Type) %>%
  summarize(n = n()) %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = reorder(Type, -n), y = n)) +
    geom_col() +
    theme_base() +
    labs(x = "Type", y = "Count", 
         title = "Asian organizations (N = 299)",
         subtitle = "Sorted by organization types")

latino_org_n <- latino_org %>%
  dplyr::select(City, Type) %>%
  group_by(Type) %>%
  summarize(n = n()) %>%
  arrange(desc(n)) %>%
  ggplot(aes(x = reorder(Type, -n), y = n)) +
    geom_col() +
    theme_base() +
    labs(x = "Type", y = "Count", 
         title = "Latino organizations (N = 519)",
         subtitle = "Sorted by organization types")

aa_org_n / latino_org_n

ggsave("/home/jae/analyzing-asian-american-latino-civic-infrastructure/outputs/asian_latino_orgs_n.png")

```
### 2.2. Time-series analysis

#### 2.2.1. Turning into time-series data 

Don't forget to fill the missing years!

```{r}

# Create the full years

asian_all_years <- seq(min(asian_org$F.year), max(asian_org$F.year))
latino_all_years <- seq(min(latino_org$F.year), max(latino_org$F.year))

# Turn it into a dataframe 

asian_all_years <- data.frame(F.year = asian_all_years)
latino_all_years <- data.frame(F.year = latino_all_years)

# Count by year and type

asian_year <- asian_org %>%
  count(F.year, States, Type) %>%
  rename(Freq = n) %>%
  right_join(asian_all_years, by = "F.year")

latino_year <- latino_org %>%
  count(F.year, States, Type) %>% 
  rename(Freq = n) %>%
  right_join(latino_all_years, by = "F.year")

```

#### 2.2.2 Plotting

```{r}

# Merge

merged <- bind_rows(mutate(asian_year, group = "Asian Americans"),
          mutate(latino_year, group = "Latinos"))

# Running total 

merged_running_total <- merged %>%
  group_by(group, Type) %>% 
  mutate(running_total = cumsum(Freq))

# Plot

merged_running_total %>%
  ggplot(aes(x = F.year, y = Freq, fill = Type)) +
    geom_col() +
    labs(x = "Year", y = "Number of organizations founded") +
    facet_wrap(~group) +
    xlim(c(1960,2017)) + 
    theme_base() 

ggsave("/home/jae/analyzing-asian-american-latino-civic-infrastructure/outputs/org_founding_year.png")

```

### 2.3. Geospatial analysis 

I adapted code from [this](https://github.com/Robinlovelace/Creating-maps-in-R), [this](https://geocompr.robinlovelace.net/adv-map.html#animated-maps) and [this](https://d4tagirl.com/2017/05/how-to-plot-animated-maps-with-gganimate) site.

#### 2.3.1. Geocoding

```{r}

# Base map

us_states <- map_data("state")
us_county <- map_data("county")

# Get state names 

asian_org$region <- tolower(abbr2state(asian_org$States))
latino_org$region <- tolower(abbr2state(latino_org$States))

# Create fuctions 

county_map <- function(data){
  data_county<- count(data, County)

  colnames(data_county)[1] <- "subregion"

  data_county$subregion <- as.character(data_county$subregion)
  data_county$subregion <- tolower(data_county$subregion)

  us_county_data <- left_join(us_county, data_county)
  return(us_county_data)
}

state_map <- function(data){
  data_state<- count(data, region)
  
  colnames(data_state)[1] <- "region"
  
  data_state$region <- as.character(data_state$region)
  data_state$region <- tolower(data_state$region)
  
  us_state_data <- left_join(us_states, data_state)
  return(us_state_data)
}

# Get state and county maps 

asian_state_map <- state_map(asian_org)
latino_state_map <- state_map(latino_org)

asian_county_map <- county_map(asian_org)
latino_county_map <- county_map(latino_org)

```

#### 2.3.2. Plotting  

##### 2.3.2.1. Static maps 

```{r}

# Asian Americans

## State

asian_state <- ggplot(data = asian_state_map,
            aes(x = long, y = lat,
                group = group, fill = n))+
  geom_polygon(color = "gray90", size = 0.05) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme_map() +
  labs(fill = "Number of organizations",
       title = "Asian American advocacy and CBOs in States (2017)")+
  theme(legend.position = "bottom") 

## County 

asian_county <- ggplot(data = asian_county_map,
            aes(x = long, y = lat,
                group = group, fill = n))+
  geom_polygon(color = "gray90", size = 0.05) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme_map() +
  labs(fill = "Number of organizations",
       title = "Asian American advocacy and CBOs in Counties (2017)")+
  theme(legend.position = "bottom") 

# Latinos 

## State

latino_state <- ggplot(data = latino_state_map,
            aes(x = long, y = lat,
                group = group, fill = n))+
  geom_polygon(color = "gray90", size = 0.05) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme_map() +
  labs(fill = "Number of organizations",
       title = "Latino advocacy and CBOs in States (2017)")+
  theme(legend.position = "bottom") 

## County 

latino_county <- ggplot(data = latino_county_map,
            aes(x = long, y = lat,
                group = group, fill = n))+
  geom_polygon(color = "gray90", size = 0.05) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme_map() +
  labs(fill = "Number of organizations",
       title = "Latino advocacy and CBOs in Counties (2017)")+
  theme(legend.position = "bottom") 

(asian_state + asian_county) / (latino_state + latino_county)

ggsave("/home/jae/analyzing-asian-american-latino-civic-infrastructure/outputs/state_county_maps.png")
```

##### 2.3.2.2. Dynamic maps 

```{r}

# Asian Americans

## County 

ggplot(data = asian_county_map,
            aes(x = long, y = lat,
                group = group, fill = n))+
  geom_polygon(color = "gray90", size = 0.05) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme_map() +
  labs(fill = "Number of organizations",
       title = "Asian American advocacy and CBOs in Counties (2017)")+
  theme(legend.position = "bottom") 

ggsave("/home/jae/analyzing-asian-american-latino-civic-infrastructure/outputs/animated_asian_county_maps.png")

```

```{r}
# Latinos 

## County 

ggplot(data = latino_county_map,
            aes(x = long, y = lat,
                group = group, fill = n))+
  geom_polygon(color = "gray90", size = 0.05) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme_map() +
  labs(fill = "Number of organizations",
       title = "Latino advocacy and CBOs in Counties (2017)")+
  theme(legend.position = "bottom") 

ggsave("/home/jae/analyzing-asian-american-latino-civic-infrastructure/outputs/animated_latino_county_map.png")

```

