---
title: "Descriptive analysis"
author: "Jae Yeon Kim"
output:
html_document:
  toc: True
  theme: united
  number_sections: True
---

## Setup

```{r}

# if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  magrittr,
  tidyverse, # the tidyverse framework
  data.table, # fast data wrangling
  patchwork, # arranging ggplots
  here, # reproducibility
  rvest, # parsing html

  ### ggplot themes
  ggsci, # pub-ready ggplots
  ggpubr, # arranging ggplots
  ggthemes, # fancy ggplot themes
  ggrepel, # annotations

  ### Spatial analysis
  tidygeocoder, # geocoding
  tigris, # shape files
  usmap,
  maps, # maps
  mapproj,
  ggsn,
  tmap,
  tmaptools,
  sf,
  leaflet, # interactive maps
  mapview, # to view and save map objects

  ### Time series analysis
  ggseas, # seasonality adjustment
  fpp2, # detecting seasonality in data

  ### Interactiev maps
  gganimate, # animated maps
  gifski # animated maps
)

# devtools::install_github("jaeyk/makereproducible")
library(makereproducible)

# Import R scripts

script_list <- list.files(paste0(here::here(), "/functions"),
  pattern = "*.r|*.R",
  full.names = TRUE
)

for (i in 1:length(script_list))
{
  source(script_list[[i]])
}

# for publication-friendly theme
theme_set(theme_pubr())
```

## Load files

N of Asian orgs: 299
N of Latino orgs: 519

```{r include=FALSE}

# Load files

asian_org <- read_csv(make_here("/home/jae/analyzing-asian-american-latino-civic-infrastructure/raw_data/asian_orgs.csv"))

latino_org <- read_csv(make_here("/home/jae/analyzing-asian-american-latino-civic-infrastructure/raw_data/latino_orgs.csv"))

asian_latino_census <- read_csv(make_here("/home/jae/analyzing-asian-american-latino-civic-infrastructure/raw_data/asian_latino_census.csv"))

reagan <- read_csv(make_here("/home/jae/analyzing-asian-american-latino-civic-infrastructure/raw_data/reagan_budget.csv"))

# Chinese service org

chinese_service_org <- read_csv(make_here("/home/jae/analyzing-asian-american-latino-civic-infrastructure/raw_data/chinese_service_org.csv"))

# Mexican service org

mexican_service_org <- read_csv(make_here("/home/jae/analyzing-asian-american-latino-civic-infrastructure/raw_data/mexican_service_org.csv"))
```

## Descriptive analysis

### Overall

```{r}

# Merge the two dfs 
orgs <- merge_by_group(asian_org, latino_org)

org_df <- orgs 

# Add decade 
org_df <- add_decade(org_df, F.year) %>%
  filter(!is.na(decade))

# Pop mass 
pop_mass_plot <- org_df %>%
  count(category, Type, decade) %>%
  ggplot(aes(x = decade, y = n, 
             fill = Type)) +
    geom_col(position = "dodge") +
    facet_wrap(~category, scales = "free") +
    theme_pubr() +
    scale_fill_npg() +
    labs(x = "Decade", 
         y = "N of organizations founded", 
         title = "Organizational founding trend (mass)")

# Pop density 

## Wrangle 
census <- asian_latino_census %>%
  filter(Year %in% c(1960:2020)) %>%
  mutate(Year = as.character(Year),
         Year = paste0(Year, "s"),
         Year = fct_relevel(Year, c("1960s", "1970s", "1980s", "1990s", "2000s", "2010s"))) %>%
  rename(decade = Year,
         category = Group)

## Join 
org_count <- org_df %>%
  count(category, Type, decade)

org_count <- left_join(org_count, census) %>%
  mutate(ratio = n/(Size/1000000))

pop_density_plot <- ggplot(org_count, aes(x = decade, y = ratio, 
             fill = Type)) +
    geom_col(position = "dodge") +
    facet_wrap(~category, scales = "free") +
    theme_pubr() +
    scale_fill_npg() +
    labs(x = "Decade", 
         y = "Same count per 1 million population", 
         title = "Organizational founding trend (density)")

pop_mass_plot / pop_density_plot

ggsave(here("outputs", "pop_mass_density.png"),
       height = 8, width = 10)

```

### Scope and naming trends 

- Setup 

```{r}
# Mutate several vars of interest 

## Name related 
org_df <- org_df %>%
  mutate(name.l = tolower(Name)) %>%
  mutate(panethnic = str_detect(name.l, "asian|hispanic|latino|latina|raza|centro|spanish") %>% as.numeric(),
         ethnic = str_detect(name.l, 
                            "chinese|chinatown| japanese|filipino|mexican|chicano|chicana|puerto|cuban"),
         unique = ifelse(panethnic == 0 & ethnic == 0, 1, 0)) %>%
  pivot_longer(cols = c(panethnic, ethnic, unique),
               names_to = "name_type",
               values_to = "name_value")

org_df$national <- factor(ifelse(str_detect(org_df$Name, "National") | org_df$States == "DC", "National", "Local")) 
```

- Scope 

```{r}

org_df %>% 
  filter(!is.na(national)) %>%
  count(national, Type, category) %>%
  mutate(
      prop = n / sum(n),
      prop = round(prop, 2)
    ) %>%
  ggplot(aes(x = fct_reorder(Type, prop), y = prop, 
             fill = national)) +
    geom_col(position = "fill") +
    facet_grid(~category, scales = "free") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_pubr() +
    scale_fill_npg() +
    labs(x = "Organizational type", y = "Proportion",
         fill = "Scope of organizational activities") 
    
ggsave(here("outputs", "national_local_trend.png"),
       height = 6, width = 8)

```

- Naming 

```{r}
org_df %>% 
  filter(name_value == 1) %>%
  mutate(name_type = factor(name_type),
         name_type = fct_relevel(name_type, c("panethnic", "ethnic", "unique"))) %>%
  mutate(name_type = str_to_title(name_type)) %>%
  count(name_type,  Type, category) %>%
  mutate(
      prop = n / sum(n),
      prop = round(prop, 2)
    ) %>%
  ggplot(aes(x = fct_reorder(Type, prop), y = prop, 
             fill = name_type)) +
    geom_col(position = "fill") +
    facet_grid(~category, scales = "free") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_pubr() +
    scale_fill_npg() +
    labs(x = "Type", y = "Proportion",
         fill = "Name type")
    
ggsave(here("outputs", "naming_trend.png"),
       height = 6, width = 8)

```

### Additional desc 

#### Turning into time-series data

```{r}

# Fill 0 years to each subset
asian_cbo_year <- org_to_ts(asian_org %>% filter(Type == "CBO"))
asian_advo_year <- org_to_ts(asian_org %>% filter(Type == "Advocacy"))
asian_hybrid_year <- org_to_ts(asian_org %>% filter(Type == "Hybrid"))

latino_cbo_year <- org_to_ts(latino_org %>% filter(Type == "CBO"))
latino_advo_year <- org_to_ts(latino_org %>% filter(Type == "Advocacy"))
latino_hybrid_year <- org_to_ts(latino_org %>% filter(Type == "Hybrid"))

# Bind them
asian_year <- bind_rows(asian_cbo_year, asian_advo_year, asian_hybrid_year)
latino_year <- bind_rows(latino_cbo_year, latino_advo_year, latino_hybrid_year)

write_csv(asian_year, make_here("/home/jae/analyzing-asian-american-latino-civic-infrastructure/processed_data/asian_year.csv"))

write_csv(latino_year, make_here("/home/jae/analyzing-asian-american-latino-civic-infrastructure/processed_data/latino_year.csv"))
```

#### Panethnic vs. Ethnic 

- 76% of Chinese CBOs remain Chinese and 24% of them turned into PCBOs. 
- 24% of Mexican CBOs remain Mexican and 76% of them turned into PCBOs.

```{r}

# Org proportions  
chinese_service_org %>% 
  count(Panethnic) %>%
  mutate(prop = n/sum(n),
         prop = round(prop, 2))

mexican_service_org %>% 
  count(Panethnic) %>%
  mutate(prop = n/sum(n),
         prop = round(prop, 2))

```

```{r}
# Plot 

pcbo_count <- org_df %>%
  count(category, Type, decade) %>%
  filter(Type == "CBO") 

ethnic_orgs <- merge_by_group_extended(chinese_service_org[,c("F.year")], mexican_service_org[,c("F.year")])

ethnic_orgs <- add_decade(ethnic_orgs, F.year) %>%
  filter(!is.na(decade))

ecbo_count <- ethnic_orgs %>%
  count(category, decade) 

df_joined <- full_join(pcbo_count, ecbo_count) %>%
  mutate(Group = ifelse(category %in% c("Asian", "Chinese"), "Asian or Chinese", "Latino or Mexican")) 

df_joined %>%
    ggplot(aes(x = decade, y = n, fill = category)) +
        geom_col(position = "dodge") +
        theme_pubr() +
        scale_fill_npg() +
        labs(x = "Decade", 
             y = "N of organizations founded",
             fill = "Type") +
        facet_wrap(~Group)

ggsave(make_here("/home/jae/analyzing-asian-american-latino-civic-infrastructure/outputs/org_founding_year_combined.png"), height = 5, width = 7)
```

## Geospatial analysis

### Prep data 

```{r}

# register_google(key = "google api key")

# Subset data
## Asian

asian_org_dt <- data.table(asian_org)

asian_address <- asian_org_dt[F.year <= 1981, .(Address, F.year, Name, Type, States, County, City), ] %>% as.data.frame()

## Latino
latino_org_dt <- data.table(latino_org)

latino_address <- latino_org_dt[F.year <= 1981, .(Address, F.year, Name, Type, States, County, City), ] %>% as.data.frame()

org_address <- merge_by_group(asian_address, latino_address)

# Export
write_csv(org_address, here("processed_data", "org_address.csv"))

org_address <- read_csv(here("processed_data", "org_address.csv"))
```

### EDA
```{r}
org_address %>%
  count(States, sort = TRUE)
# California = 79, DC = 11, NY = 11

org_address %>%
  count(States, category, sort = TRUE)
# California - Asian = 43, California - Latino = 36

org_address %>%
  count(County, sort = TRUE)
# San Francisco 25, Los Angeles 19, Alameda 10, Sacramento 7

org_address %>%
  count(County, category, sort = TRUE)
# San Francisco - Asian = 20, Los Angeles - Asian = 10, Alameda - Asian = 5, Los Angeles - Latino = 9, Alameda - Asian 5, Alameda - Latino 5
```

### Import geocodes 

```{r}
# Fix the problematic addresses using Bing (done in Python)
lat_longs <- read_csv(here("processed_data", "org_lat_logs_fixed.csv"))[, -1]
```

### Making maps

#### Bubble map 

```{r}

# Join the two data
df <- left_join(org_address, lat_longs)

# Filter; Data ready
df <- df %>%
  filter(category == "Asian") %>%
  filter(!is.na(Address)) %>%
  filter(City == toupper("San Francisco"))

# Turn df into sf object
sites <- sf::st_as_sf(df,
  coords = c(
    "longtitude",
    "latitude"
  ),
  crs = 4326,
  agr = "identity"
)

# Import Bay Area shape file

bay_area_sf <- tigris::tracts(
  state = "CA",
  county = c("San Francisco")
)

# Crop the coordinates
cropped_sf <- st_crop(bay_area_sf,
  xmin = -122.48,
  xmax = -122.34,
  ymin = 37.76,
  ymax = 37.83
)

# For the test
# ggplot(bay_area_sf) +
#     geom_sf() +
#     ggplot2::coord_sf(xlim = c(-122.48, -122.34),
#                       ylim = c(37.76, 37.83)) +
#     theme_bw()

# Set the CRS
cropped_sf <- st_set_crs(cropped_sf, 4326)

# tmap approach
bay_tmap <-
  tm_shape(cropped_sf) +
  tm_borders() +
  tm_shape(sites) +
  tm_bubbles(
    size = 1,
    shapeNA = NA,
    col = "Type"
  ) +
  tm_layout(title = "Asian American organizations in San Francisco")

# to change color palette  tmaptools::palette_explorer()

# Static mode
tmap_mode("plot")

tmap_save(bay_tmap, file = here("outputs", "asian_org_map.png"))

# Interactive mode (leaflet)
lf <- tmap_leaflet(bay_tmap) %>%
  addTiles()

mapshot(lf,
  file = here("outputs", "asian_org_map_interactive.png"),
  remove_controls = c("homeButton", "layersControl")
)
```

#### Heatmap 

```{r}

# Load usmap
us_map <- usmap::us_map()

# Wrangle data
org_addr_rn <- org_address %>%
  rename(
    state = States,
    county = County
  ) %>%
  group_by(state, category) %>%
  count()

asian_map_df <- org_addr_rn %>% filter(category == "Asian")

latino_map_df <- org_addr_rn %>% filter(category != "Asian")
```

```{r}
# Map
asian_org_plot <- plot_us_heatmap(asian_map_df) + labs(title = "Asian American organizations")

latino_org_plot <- plot_us_heatmap(latino_map_df) + labs(title = "Latino organizations")

asian_org_plot + latino_org_plot

ggsave(here("outputs", "heatmaps.png"),
  width = 14,
  height = 7
)
```
