---
title: "Additional robustness check"
author: "Jae Yeon Kim"
output:
html_document:
  toc: True
  theme: united
  number_sections: True
---

# Setup 

```{r, echo=FALSE}

# Import libraries 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
        tidyverse, # the tidyverse framework
        patchwork, # arranging ggplots 
        ggpubr, # arranging ggplots 
        ggthemes, # fancy ggplot themes
        broom, # modeling
        here, # reproducibility 
        magrittr, # %<>%
        nlme, # GLS
        stargazer) # latex table 
        
# devtools::install_github("jaeyk/makereproducible")
library(makereproducible)

# Import R scripts

script_list <- list.files(paste0(here::here(), "/functions"),
  pattern = "*.r|*.R",
  full.names = TRUE
)

for (i in 1:length(script_list))
{
  source(script_list[[i]])
}

# for publication-friendly theme
theme_set(theme_pubr())

```
# Load files and wrangle data 

```{r}

wop_asian_city <- read_csv(here("raw_data", "asian_orgs.csv")) %>%
  filter(F.year <= 1981) %>%
  mutate(County = trimws(County)) %>%
  count(City, County, States, Type) 

wop_latino_city <- read_csv(here("raw_data", "latino_orgs.csv")) %>%
  filter(F.year <= 1981) %>%
  mutate(County = trimws(County)) %>%
  count(City, County, States, Type) 

oeo_census <- read.csv(here("processed_data" , "oeo_census.csv"))

historical_census_county <- read_csv(here("processed_data", "historical_census_county.csv")) %>%
  mutate(County = toupper(County)) %>%
  filter(County != "STATE TOTAL") %>%
  mutate(County = trimws(County)) 

historical_census_county <- add_state_abb(historical_census_county) %>%
    select(State, County, year, poverty_rate, pop_size, State_abb)

names(historical_census_county)

activism <- read.csv(here("processed_data", "activism.csv"))[,-1]

```

# Merge data

- 183 obs

```{r}

df1 <- merge_by_group(wop_asian_city, wop_latino_city)

df1$Type[df1$Type == "Hybrid"] <- "CBO"

df2 <- df1 %>% left_join(activism)

df3 <- left_join(df2, oeo_census, by = c("County" , "States" , "City"))

df4 <- left_join(df3, historical_census_county %>% filter(year == 1980), 
        by = c("County",
               "States" = "State_abb")) %>%
  filter(year == 1980) %>%
  distinct(OEO_fund, poverty_rate, Asian_per, Latino_per, pop_size, Type, category, n, Activism)

```

# Model data 

```{r}

df4 %<>%
  mutate(category = factor(category),
         Activism = factor(Activism),
         Asian_per = as.numeric(Asian_per),
         Latino_per = as.numeric(Latino_per),
         OEO_fund = scales::rescale(OEO_fund, to = c(0,100)),
         pop_size = scales::rescale(pop_size, to = c(0,100)),
         log_n = log(n))
```

OLS AIC:960.343
Logged OLS AIC:359.812
Poisson AIC:762.82
Negative binomial AIC:762.047

```{r}
lm.out <- lm(n ~ OEO_fund + poverty_rate + Asian_per + Latino_per + pop_size + Type + category + Activism, data = df4)

lm_log.out <- lm(log_n ~ OEO_fund + poverty_rate + Asian_per + Latino_per + pop_size + Type + category + Activism, data = df4)

poisson.out <- glm(n ~ OEO_fund + poverty_rate + Asian_per + Latino_per + pop_size + Type + category + Activism, data = df4, family = "poisson")

nb.out <- MASS::glm.nb(n ~ OEO_fund + poverty_rate + Asian_per + Latino_per + pop_size + Type + category + Activism, data = df4)

```

```{r}
cat(paste0("OLS AIC:", round(AIC(lm.out), 3), "\n",   
           "Logged OLS AIC:", round(AIC(lm_log.out), 3), "\n",
           "Poisson AIC:", round(AIC(poisson.out), 3), "\n",
           "Negative binomial AIC:", round(AIC(nb.out), 3)))
      
```
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{log\_n} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
 OEO\_fund & 0.006$^{***}$ & 0.005$^{***}$ & 0.005$^{***}$ & 0.006$^{***}$ \\ 
  & (0.002) & (0.002) & (0.002) & (0.002) \\ 
  & & & & \\ 
 TypeCBO & 0.277$^{***}$ & 0.278$^{***}$ & 0.361$^{***}$ & 0.409$^{***}$ \\ 
  & (0.083) & (0.083) & (0.083) & (0.082) \\ 
  & & & & \\ 
 categoryLatino & $-$0.393$^{***}$ & $-$0.392$^{***}$ & $-$0.341$^{***}$ & $-$0.333$^{***}$ \\ 
  & (0.067) & (0.067) & (0.068) & (0.066) \\ 
  & & & & \\ 
 poverty\_rate &  & 0.001 & $-$0.006 & $-$0.003 \\ 
  &  & (0.005) & (0.006) & (0.006) \\ 
  & & & & \\ 
 Asian\_per &  &  & 0.008$^{**}$ & 0.002 \\ 
  &  &  & (0.004) & (0.004) \\ 
  & & & & \\ 
 Latino\_per &  &  & 0.013$^{***}$ & 0.004 \\ 
  &  &  & (0.004) & (0.005) \\ 
  & & & & \\ 
 pop\_size &  &  &  & 0.001 \\ 
  &  &  &  & (0.001) \\ 
  & & & & \\ 
 Activism1 &  &  &  & 0.360$^{***}$ \\ 
  &  &  &  & (0.077) \\ 
  & & & & \\ 
 Constant & 0.238$^{**}$ & 0.228$^{*}$ & 0.035 & $-$0.069 \\ 
  & (0.102) & (0.124) & (0.129) & (0.129) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 264 & 264 & 264 & 258 \\ 
R$^{2}$ & 0.186 & 0.186 & 0.242 & 0.325 \\ 
Adjusted R$^{2}$ & 0.177 & 0.173 & 0.224 & 0.303 \\ 
Akaike Inf. Crit. & 377.708 & 379.688 & 364.961 & 335.196 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

```{r}

m1 <- lm(log_n ~ OEO_fund + Type + category, data = df4)

m2 <- lm(log_n ~ OEO_fund + Type + category + poverty_rate, data = df4)

m3 <- lm(log_n ~ OEO_fund + Type + category + poverty_rate + Asian_per + Latino_per, data = df4)

m4 <- lm(log_n ~ OEO_fund + Type + category + poverty_rate + Asian_per + Latino_per + pop_size + Activism, data = df4)

stargazer::stargazer(add_AIC(m1), add_AIC(m2), add_AIC(m3), add_AIC(m4),
                     keep.stat = c(
                       "AIC", "rsq", "n", "adj.rsq"))

```

