---
title: "Additional robustness check"
author: "Jae Yeon Kim"
output:
html_document:
  toc: True
  theme: united
  number_sections: True
---

# Setup 

```{r, echo=FALSE}

# Import libraries 

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
        readstata13, # import stata 13 files 
        tidyverse, # the tidyverse framework
        patchwork, # arranging ggplots 
        ggpubr, # arranging ggplots 
        ggthemes, # fancy ggplot themes
        broom, # modeling
        here, # reproducibility 
        magrittr, # %<>%
        nlme, # GLS
        stargazer, # latex table 
        lmtest,
        sandwich)
  
# devtools::install_github("jaeyk/makereproducible")
library(makereproducible)

# Import R scripts

script_list <- list.files(paste0(here::here(), "/functions"),
  pattern = "*.r|*.R",
  full.names = TRUE
)

for (i in 1:length(script_list))
{
  source(script_list[[i]])
}

# for publication-friendly theme
theme_set(theme_pubr())

```
# Load files and wrangle data 

```{r}

wop_asian_city <- read_csv(here("raw_data", "asian_orgs.csv")) %>%
  filter(F.year <= 1981) %>%
  mutate(County = trimws(County)) %>%
  count(City, County, States, Type) 

wop_latino_city <- read_csv(here("raw_data", "latino_orgs.csv")) %>%
  filter(F.year <= 1981) %>%
  mutate(County = trimws(County)) %>%
  count(City, County, States, Type) 

oeo_census <- read.csv(here("processed_data" , "oeo_census.csv"))

historical_census_county <- read_csv(here("processed_data", "historical_census_county.csv")) %>%
  mutate(County = toupper(County)) %>%
  filter(County != "STATE TOTAL") %>%
  mutate(County = trimws(County)) 

historical_census_county <- add_state_abb(historical_census_county) %>%
    select(State, County, year, poverty_rate, pop_size, State_abb) %>%
  filter(year == 1980)

```

# Merge data

- N of obs: 95 counties 

```{r}

df1 <- merge_by_group(wop_asian_city, wop_latino_city) # 67 counties 

df1$Type[df1$Type == "Hybrid"] <- "CBO"

df2 <- left_join(df1, oeo_census, by = c("County" , "States" , "City"))

df3 <- left_join(df2, historical_census_county, 
        by = c("County",
               "States" = "State_abb"))

```

# Model data 

```{r}

df3 <- df3 %<>%
  mutate(category = factor(category),
         Asian_per = as.numeric(Asian_per),
         Latino_per = as.numeric(Latino_per),
         OEO_per = round(df3$OEO_fund/sum(df3$OEO_fund, na.rm = TRUE),2)*100,
         pop_size = scales::rescale(pop_size, to = c(0,100)),
         log_n = log(n))

```

```{r}
df3 <- replace_na(df3, 
                  list(Asian_per = 0, 
                       Latino_per = 0, 
                       OEO_fund = 0, 
                       OEO_per = 0, 
                       pop_size = 0, 
                       poverty_rate = 0)
                  )

```

OLS AIC:413.191
Logged OLS AIC:167.942
Poisson AIC:336.547
Negative binomial AIC:337.276

```{r}
lm.out <- lm(n ~ OEO_per + poverty_rate + Asian_per + Latino_per + pop_size + Type + category, data = df3)

lm_log.out <- lm(log_n ~ OEO_per + poverty_rate + Asian_per + Latino_per + pop_size + Type + category, data = df3)

poisson.out <- glm(n ~ OEO_per + poverty_rate + Asian_per + Latino_per + pop_size + Type + category, data = df3, family = "poisson")

nb.out <- MASS::glm.nb(n ~ OEO_per + poverty_rate + Asian_per + Latino_per + pop_size + Type + category, data = df3)

```

```{r}
cat(paste0("OLS AIC:", round(AIC(lm.out), 3), "\n",   
           "Logged OLS AIC:", round(AIC(lm_log.out), 3), "\n",
           "Poisson AIC:", round(AIC(poisson.out), 3), "\n",
           "Negative binomial AIC:", round(AIC(nb.out), 3)))
      
```
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{3}{c}{\textit{OLS}} & \textit{coefficient} \\ 
 & \multicolumn{3}{c}{\textit{}} & \textit{test} \\ 
 & Model 1 & Model 2 & Model 3 & Model 4 \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\\[-1.8ex] & m1 & m2 & m3 & lm_white\\ 
\hline \\[-1.8ex] 
 OEO\_per & 0.122$^{**}$ (0.056) & 0.118$^{**}$ (0.055) & 0.116$^{**}$ (0.056) & 0.116$^{*}$ (0.060) \\ 
  TypeCBO & 0.163 (0.135) & 0.190 (0.135) & 0.221 (0.140) & 0.221$^{*}$ (0.129) \\ 
  categoryLatino & $-$0.262$^{**}$ (0.106) & $-$0.207$^{*}$ (0.109) & $-$0.231$^{**}$ (0.112) & $-$0.231$^{*}$ (0.124) \\ 
  Asian\_per &  & 0.011$^{*}$ (0.007) & 0.011 (0.007) & 0.011 (0.013) \\ 
  Latino\_per &  & 0.002 (0.005) & 0.008 (0.007) & 0.008 (0.007) \\ 
  poverty\_rate &  &  & $-$0.006 (0.010) & $-$0.006 (0.010) \\ 
  pop\_size &  &  & $-$0.002 (0.002) & $-$0.002 (0.002) \\ 
  Constant & 0.213 (0.162) & 0.077 (0.183) & 0.119 (0.209) & 0.119 (0.194) \\ 
 \hline \\[-1.8ex] 
Observations & 111 & 111 & 111 &  \\ 
R$^{2}$ & 0.118 & 0.146 & 0.155 &  \\ 
Adjusted R$^{2}$ & 0.094 & 0.105 & 0.097 &  \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 

```{r}

m1 <- lm(log_n ~ OEO_per + Type + category, data = df3)

m2 <- lm(log_n ~ OEO_per + Type + category + Asian_per + Latino_per, data = df3)

m3 <- lm(log_n ~ OEO_per + Type + category + Asian_per + Latino_per + poverty_rate + pop_size, data = df3)

lm_white <- coeftest(m3, vcov = vcovHC(m3, type = "HC0"))

stargazer::stargazer(m1, m2, m3, lm_white,
                     keep.stat = c(
                       "rsq", "n", "adj.rsq"),
                     single.row = TRUE, 
                     object.names = TRUE, 
                     column.labels = c("Model 1",
                                       "Model 2",
                                       "Model 3",
                                       "Model 4"),
                     dep.var.labels.include = FALSE)


```

